Note on: Tightness of Upper Bounds on PPR Misclassification Error

### 2021-12-23 notes/weekly_notes/12.3.20.NotesForWeek.tex

\documentclass{report}
\usepackage{amsmath}
\usepackage{amsfonts, amsthm, amssymb}
\usepackage{graphicx}
\usepackage[colorlinks]{hyperref}
\usepackage[parfill]{parskip}
\usepackage{algpseudocode}
\usepackage{algorithm}
\usepackage{enumerate}
\usepackage[shortlabels]{enumitem}
\usepackage{fullpage}
\usepackage{mathtools}
\usepackage{subcaption}
\usepackage{tikz}

@@

\DeclarePairedDelimiterX{\norm}[1]{\lVert}{\rVert}{#1}

\newcommand{\eqdist}{\ensuremath{\stackrel{d}{=}}}
\newcommand{\Graph}{\mathcal{G}}
\newcommand{\Reals}{\mathbb{R}}
\newcommand{\Identity}{\mathbb{I}}
\newcommand{\Xsetistiid}{\overset{\text{i.i.d}}{\sim}}
\newcommand{\convprob}{\overset{p}{\to}}
\newcommand{\convdist}{\overset{w}{\to}}
\newcommand{\Expect}[1]{\mathbb{E}\left[ #1 \right]}
\newcommand{\Risk}[2][P]{\mathcal{R}_{#1}\left[ #2 \right]}
\newcommand{\Prob}[1]{\mathbb{P}\left( #1 \right)}
\newcommand{\iset}{\mathbf{i}}
\newcommand{\jset}{\mathbf{j}}
\newcommand{\myexp}[1]{\exp \{ #1 \}}
\newcommand{\abs}[1]{\left \lvert #1 \right \rvert}
\newcommand{\restr}[2]{\ensuremath{\left.#1\right|_{#2}}}
\newcommand{\ext}[1]{\widetilde{#1}}
\newcommand{\set}[1]{\left\{#1\right\}}
\newcommand{\seq}[1]{\set{#1}_{n \in \N}}
\newcommand{\Xsetotp}[2]{\langle #1, #2 \rangle}
\newcommand{\floor}[1]{\left\lfloor #1 \right\rfloor}
\newcommand{\Var}{\mathrm{Var}}
\newcommand{\Cov}{\mathrm{Cov}}
\newcommand{\Xsetiam}{\mathrm{diam}}

\newcommand{\emC}{C_n}
\newcommand{\emCpr}{C'_n}
\newcommand{\emCthick}{C^{\sigma}_n}
\newcommand{\emCprthick}{C'^{\sigma}_n}
\newcommand{\emS}{S^{\sigma}_n}
\newcommand{\estC}{\widehat{C}_n}
\newcommand{\hC}{\hat{C^{\sigma}_n}}
\newcommand{\vol}{\mathrm{vol}}
\newcommand{\spansp}{\mathrm{span}~}
\newcommand{\1}{\mathbf{1}}

\newcommand{\Linv}{L^{\Xsetagger}}
\DeclareMathOperator*{\argmin}{argmin}
\DeclareMathOperator*{\argmax}{argmax}

@@

%%% Vectors
\newcommand{\thetast}{\theta^{\star}}
\newcommand{\betap}{\beta^{(p)}}
\newcommand{\betaq}{\beta^{(q)}}
\newcommand{\vardeltapq}{\varDelta^{(p,q)}}

%%% Matrices
\newcommand{\X}{X} % no bold
\newcommand{\Y}{Y} % no bold
\newcommand{\Z}{Z} % no bold
\newcommand{\Lgrid}{L_{\grid}}
\newcommand{\Xsetgrid}{D_{\grid}}
\newcommand{\Linvgrid}{L_{\grid}^{\Xsetagger}}
\newcommand{\Lap}{{\bf L}}
\newcommand{\NLap}{{\bf N}}
\newcommand{\PLap}{{\bf P}}

%%% Sets and classes
\newcommand{\Xset}{\mathcal{X}}
\newcommand{\Sset}{\mathcal{S}}
\newcommand{\Hclass}{\mathcal{H}}
\newcommand{\Pclass}{\mathcal{P}}
\newcommand{\Leb}{L}
\newcommand{\mc}[1]{\mathcal{#1}}

@@

%%% Operators
\newcommand{\Tadj}{T^{\star}}
\newcommand{\Xsetive}{\mathrm{div}}
\newcommand{\Xsetif}{\mathop{}\!\mathrm{d}}
\newcommand{\gradient}{\mathcal{D}}
\newcommand{\Hessian}{\mathcal{D}^2}
\newcommand{\dotp}[2]{\langle #1, #2 \rangle}
\newcommand{\Dotp}[2]{\Bigl\langle #1, #2 \Bigr\rangle}

%%% Misc
\newcommand{\grid}{\mathrm{grid}}
\newcommand{\critr}{R_n}
\newcommand{\Xsetx}{\,dx}
\newcommand{\Xsety}{\,dy}
\newcommand{\Xsetr}{\,dr}
\newcommand{\Xsetxpr}{\,dx'}
\newcommand{\Xsetypr}{\,dy'}
\newcommand{\wt}[1]{\widetilde{#1}}
\newcommand{\wh}[1]{\widehat{#1}}
\newcommand{\ol}[1]{\overline{#1}}
\newcommand{\spec}{\mathrm{spec}}
\newcommand{\LE}{\mathrm{LE}}
\newcommand{\LS}{\mathrm{LS}}
\newcommand{\OS}{\mathrm{OS}}
\newcommand{\PLS}{\mathrm{PLS}}
\newcommand{\dist}{\mathrm{dist}}

%%% Order of magnitude
\newcommand{\soom}{\sim}

% \newcommand{\span}{\textrm{span}}

\newtheoremstyle{alden}
{6pt} % Space above
{6pt} % Space below
{} % Body font
{} % Indent amount
{\bfseries} % Theorem head font
{.} % Punctuation after theorem head
{.5em} % Space after theorem head
{} % Theorem head spec (can be left empty, meaning `normal')

\theoremstyle{alden}

\newtheoremstyle{aldenthm}
{6pt} % Space above
{6pt} % Space below
{\itshape} % Body font
{} % Indent amount
{\bfseries} % Theorem head font
{.} % Punctuation after theorem head
{.5em} % Space after theorem head
{} % Theorem head spec (can be left empty, meaning `normal')

\theoremstyle{aldenthm}
\newtheorem{theorem}{Theorem}
\newtheorem{conjecture}{Conjecture}
\newtheorem{lemma}{Lemma}
\newtheorem{example}{Example}
\newtheorem{corollary}{Corollary}
\newtheorem{proposition}{Proposition}
\newtheorem{assumption}{Assumption}
\newtheorem{remark}{Remark}

@@

\begin{document}
\title{Work for revision of ``Local Spectral Clustering of Density Upper Level Sets''}
\author{Alden Green}
\date{\today}
\maketitle

\chapter{Normalized cut}
To recall, our upper bound on normalized cut---ignoring the terms that depend on the density---is 
\begin{equation*}
\wt{\Phi}_{\nu,r}(\mc{C}_{\sigma}) \lessapprox \frac{16dr}{9\sigma}.
\end{equation*}
\section{Lower bound on normalized cut}
Our goal is to examine the tightness of our upper bound on normalized cut (Theorem 10 of our JMLR submission), by giving a comparable lower bound. Recall that the (uniform, population level) normalized cut of a set $\mc{C}_{\sigma}$ is given by
\begin{equation*}
\Phi_{\nu,r}(\mc{C}_{\sigma}) := \frac{\int_{\mc{C}_{\sigma}} \nu(B(x,r) \setminus \mc{C}_{\sigma}) \,dx}{\int_{\mc{C}_{\sigma}} \nu(B(x,r)) \,dx}.
\end{equation*}
As informed by the isoperimetric ratio, the worst-case for a functional like normalized cut should be when $\mc{C}_{\sigma}$ by a $d$-dimensional ball. Letting $\mc{C}_{\sigma} = B(0,\sigma)$, we have that
\begin{equation*}
\frac{\int_{\mc{C}_{\sigma}} \nu(B(x,r) \setminus \mc{C}_{\sigma}) \,dx}{\int_{\mc{C}_{\sigma}} \nu(B(x,r)) \,dx} = \frac{1}{\nu_d^2 r^d \sigma^d} \int_{\mc{C}_{\sigma}} \nu(B(x,r) \setminus \mc{C}_{\sigma}) \,dx.
\end{equation*}
If $\|x\| < \sigma - r$, then $B(x,r) \setminus \mc{C}_{\sigma} = \emptyset$. Otherwise $\sigma - r \leq \|x\| \leq \sigma$, and if $r \ll \sigma$ then $B(x,r) \setminus \mc{C}_{\sigma} \approx \mathrm{cap}_{r}(\|x\| - (\sigma - r))$. Converting to polar coordinates, we have:
\begin{align*}
\int_{\mc{C}_{\sigma}} \nu(B(x,r) \setminus \mc{C}_{\sigma}) \,dx & \approx s_d \int_{\sigma - r}^{\sigma} \nu(\mathrm{cap}_{r}(x - (\sigma - r))) t^{d - 1} \,dt \\
& \geq s_d (\sigma - r)^{d - 1} \int_{\sigma - r}^{\sigma} \nu(\mathrm{cap}_{r}(t - (\sigma - r)))  \,dt \\
& = s_d (\sigma - r)^{d - 1} \int_{0}^{r} \nu(\mathrm{cap}_{r}(z)  \,dz.
\end{align*}
As calculated below~\eqref{eqn:lb_conductance_1}, $\int_{0}^{r} \nu(\mathrm{cap}_{r}(z)  \,dz = \frac{1}{d + 1} \nu_d r^{d + 1} \frac{\Gamma(d/2 + 1)}{\Gamma(d/2 + 1/2)\sqrt{\pi}} \approx \frac{1}{d + 1} \nu_d r^{d + 1} \frac{\sqrt{d + 2}}{\sqrt{2\pi}}$ and hence
\begin{equation*}
\Phi_{\nu,r}(\mc{C}_{\sigma}) \approx s_d (\sigma - r)^{d - 1}\frac{1}{d + 1} \nu_d r^{d + 1} \frac{\sqrt{d + 2}}{\sqrt{2\pi}} \frac{1}{\nu_d^2 r^d \sigma^d} \approx \frac{ \sqrt{d + 2}}{(d + 1)\sqrt{2\pi}} \cdot \frac{dr}{\sigma}.
\end{equation*}
By contrast, our upper bound is $\approx dr/\sigma$, revealing a gap of roughly $\frac{ \sqrt{d + 2}}{(d + 1)\sqrt{2\pi}}$.

\chapter{Lower bound for conductance of continuous-space ball walk}
For $x \in \mc{C}_{\sigma}$ and measurable $\Sset \subseteq \mc{C}_{\sigma}$, let $\ell_{\nu,r}(x) = \nu(B(x,r) \cap \mc{C}_{\sigma})$ and ${J}_{\nu,r}(\mc{S}) = \int_{\mc{S}} \ell_{\nu,r}(x) \,dx$. Further define
\begin{equation*}
\widetilde{P}_{\nu,r}(x; \Sset) := \frac{\nu(\Sset \cap B(x,r))}{\nu(\mc{C}_{\sigma} \cap B(x,r))}, \quad \widetilde{\pi}_{\nu,r}(\Sset) = \frac{J_{\nu,r}(\mc{S})}{J_{\nu,r}(\mc{C}_{\sigma})}, \quad  \widetilde{Q}_{\nu,r}(\Sset_1,\Sset_2) := \int_{\Sset_1} \widetilde{P}_{\nu,r}(x;\Sset_2) \,d\widetilde{\pi}_{\nu,r}(x).
\end{equation*}
The uniform continuous normalized cut and conductance are then
\begin{equation*}
\widetilde{\Phi}_{\nu,r}(\Sset) := \frac{\widetilde{Q}_{\nu,r}(\Sset, \Sset^c)}{\min\set{\widetilde{\pi}_{\nu,r}(\Sset),\widetilde{\pi}_{\nu,r}(\Sset^c)}}, \quad \widetilde{\Phi}_{\nu,r} := \min_{\Sset \subseteq \mc{C}_{\sigma}} \widetilde{\Phi}_{\nu,r}(\Sset),
\end{equation*}
where the minimum is taken over all measurable sets $\Sset \subseteq \mc{C}_{\sigma}$.

\begin{lemma}
	\label{lem: uniform_continuous_conductance}
	Let $\mc{C}_{\sigma}$ satisfy Assumption \textcolor{red}{(A3)} (of our main document) for some convex set $\mathcal{K}$ with diameter $\rho$, and measure-preserving mapping $g: \mathcal{K} \to \mc{C}_{\sigma}$ with Lipschitz constant $L$. Let $0 < \ell < 1/2$ be a number that satisfies $\ell_{\nu,r}(x) \geq \nu_d r^d \ell$ for all $x \in \mc{C}_{\sigma}$.  Then the uniform conductance $\widetilde{\Phi}_{\nu,r}$ is lower bounded:
	\begin{equation*}
	\widetilde{\Phi}_{\nu,r} \geq \Bigl(1 - \frac{r}{4\rho}\Bigr) \cdot\frac{\ell^2\sqrt{2\pi}}{9} \cdot \frac{r}{\rho L \sqrt{d + 2}}
	\end{equation*}
\end{lemma}
Lemma~\ref{lem: overlap_balls} gives the lower bound $\ell \geq 1/2 \cdot (1 - r/\sigma \cdot \sqrt{(d + 2)/(2\pi)})$ leading to the following corollary.
\begin{corollary}
	\label{cor: uniform_continuous_conductance}
	Let $\mc{C}_{\sigma}$ satisfy Assumption \textcolor{red}{(A3)} for some convex set $\mathcal{K}$ with diameter $\rho$, and measure-preserving mapping $g: \mathcal{K} \to \mc{C}_{\sigma}$ with Lipschitz constant $L$. Then the uniform conductance $\widetilde{\Phi}_{\nu,r}$ is lower bounded:
	\begin{equation*}
	\widetilde{\Phi}_{\nu,r} \geq \Bigl(1 - \frac{r}{4\rho}\Bigr) \Bigl(1 - \frac{r}{\sigma}\sqrt{\frac{d + 2}{2\pi}}\Bigr)^2 \cdot \frac{\sqrt{2\pi}}{36} \cdot \frac{r}{\rho L \sqrt{d + 2}}
	\end{equation*}
\end{corollary}

\subsection{Proof of Lemma~\ref{lem: uniform_continuous_conductance}}
Lower bounds on the conductance of geometric random walks follow a typical pattern, in which one supplies an isoperimetric inequality, uses this to lower bound the ergodic flow $\wt{Q}$, and thereby derives a lower bound on the conductance. The proof of Lemma~\ref{lem: uniform_continuous_conductance} proceeds along these lines, and we start by sketching the chain of inequalities we will use. For a given partition $\{\mc{S},\mc{R}\}$ of $\mc{C}_{\sigma}$, write
\begin{equation*}
\mc{S}^{\delta} := \biggl\{u \in \mc{S}: \wt{P}(u,\mc{R}) \leq \delta \biggr\}~~\textrm{and}~~\mc{R}^{\delta} := \biggl\{u \in \mc{R}: \wt{P}(u,\mc{S}) \leq \delta \biggr\} 
\end{equation*}
where $\delta$ is a small number we will determine later on. Let $\mc{S}_{\delta} := \mc{C}_{\sigma} \setminus (\mc{S}^{\delta} \cup \mc{R}^{\delta})$. 
\begin{enumerate}
	\item[1.] The ergodic flow $\wt{Q}$ between $\mc{S}$ and $\mc{R}$ satisfies the following lower bound:
	\begin{equation*}
	\wt{Q}_{\nu,r}(\mc{S},\mc{R}) \geq \frac{1}{2} \wt{\pi}_{\nu,r}(\mc{S}_{\delta}) \cdot \delta.
	\end{equation*}
	\item[2.] For any $\mc{S} \subseteq \mc{C}_{\sigma}$, it holds that
	\begin{equation*}
	\frac{\nu(\mc{S})}{\nu(\mc{C}_{\sigma})} \cdot \ell \leq \wt{\pi}_{\nu,r}(\mc{S}) \leq \frac{\nu_d r^d \nu(\mc{S})}{I(\mc{C}_{\sigma})}
	\end{equation*}
	\item[3.] From \textcolor{red}{Abbasi-Yadkori} (see also the seminal works of \textcolor{red}{(Lovasz and Simonovits)} and \textcolor{red}{(Dyer)}), we have the following isoperimetric inequality.
	\begin{lemma}[Isoperimetry of Lipschitz embeddings of convex sets.]
		\label{lem: nonconvex_isoperimetry}
		Let $\mc{C}_{\sigma}$ satisfy Assumption \textcolor{red}{(A3)} for some convex set $\mathcal{K}$ with diameter $\rho$, and measure-preserving mapping $g: \mathcal{K} \to \mc{C}_{\sigma}$ with Lipschitz constant $L$. Then, for any partition $(\Omega_1,\Omega_2,\Omega_3)$ of $\mc{C}_{\sigma}$, 
		\begin{equation*}
		\nu(\Omega_3) \geq 2\frac{\dist(\Omega_1, \Omega_2)}{\rho L} \min(\nu(\Omega_1), \nu(\Omega_2)).
		\end{equation*}
	\end{lemma}
	\item[4.] 
	The following Lemma relates the Euclidean distance $\|x - y\|$ to the the total variation distance
	\begin{equation*}
	\|\wt{P}(x,\cdot) - \wt{P}(y,\cdot)\|_{\mathrm{TV}} = \sup_{\mc{S} \subseteq \mc{C}_{\sigma}} |\wt{P}(x,\mc{S}) - \wt{P}(y,\mc{S}) |
	\end{equation*}
	\begin{lemma}
		\label{lem: one_step_distributions}
		For all $x,y \in \mc{C}_{\sigma}$ and any $\mc{S} \in \mc{C}_{\sigma}$, it holds that
		\begin{equation}
		\label{eqn:one_step_distributions_1}
		\|x - y\| \geq \Bigl(\bigl|\wt{P}(x,\mc{S}) - \wt{P}(y,\mc{S})\bigr|\Bigr)\sqrt{\frac{2\pi}{d + 2}}r\ell
		\end{equation}
		Therefore, for any $\mc{S}_1,\mc{S}_2 \subseteq \mc{C}_{\sigma}$, it holds that
		\begin{equation}
		\label{eqn:one_step_distributions_2}
		\dist(\mc{S}_1,\mc{S}_2) \geq \Bigl(\inf_{\substack{x \in \mc{S}_1 \\ y \in \mc{S}_2}}\|\wt{P}(x,\cdot) - \wt{P}(y,\cdot)\|_{\mathrm{TV}}\Bigr)\sqrt{\frac{2\pi}{d + 2}}r\ell.
		\end{equation}
	\end{lemma}
	Note that for any $x \in \mc{S}^{\delta}, y \in \mc{R}^{\delta}$, we have that
	\begin{equation*}
	\wt{P}(x,\mc{S}) - \wt{P}(y,\mc{S}) = 1 - \bigl(\wt{P}(x,\mc{R}) + \wt{P}(y,\mc{S})\bigr) \geq 1 - 2\delta,
	\end{equation*}
	Thus, applying Lemma~\ref{lem: one_step_distributions} to $\mc{S}^{\delta}$ and $\mc{R}^{\delta}$ gives
	\begin{equation*}
	\dist(\mc{S}^{\delta},\mc{R}^{\delta}) \geq \bigl(1 - 2\delta\bigr) \cdot \sqrt{\frac{2\pi}{d + 2}}r\ell
	\end{equation*}
\end{enumerate}
The claim of Lemma~\ref{lem: uniform_continuous_conductance}---i.e. a lower bound on the continuous normalized cut $\wt{\Phi}_{\nu,r}(\mc{S})$ that holds for any measurable $\mc{S} \subseteq \mc{C}_{\sigma}$---directly follows from these inequalities, as we now show. In particular, the ergodic flow $\wt{Q}(\mc{S},\mc{R})$ can be lower bounded
\begin{equation*}
\wt{Q}_{\nu,r}(\mc{S},\mc{R}) \geq \frac{1}{2}\wt{\pi}_{\nu,r}(\mc{S}_{\delta}) \cdot \delta. \tag{Step 1}
\end{equation*}
Now, suppose $\wt{\pi}_{\nu,r}(\mc{S}^{\delta}) \leq (1 - a) \wt{\pi}_{\nu,r}(\mc{S})$ or $\wt{\pi}_{\nu,r}(\mc{R}^{\delta}) \leq (1 - a) \wt{\pi}_{\nu,r}(\mc{R})$, for some $0 < a < 1$. Then $\wt{\pi}_{\nu,r}(\mc{S}_{\delta}) \geq a \min\{\wt{\pi}_{\nu,r}(\mc{S}),\wt{\pi}_{\nu,r}(\mc{R})\}$, and consequently,
\begin{equation*}
\wt{\Phi}_{\nu,r}(\mc{S}) = \frac{\wt{Q}_{\nu,r}(\mc{S},\mc{S}^c)}{\min\{\wt{\pi}_{\nu,r}(\mc{S}),\wt{\pi}_{\nu,r}(\mc{R})\}} \geq \frac{1}{2}a \delta.
\end{equation*}
Otherwise, we deduce that
\begin{align*}
\wt{Q}_{\nu,r}(\mc{S},\mc{R}) & \geq \frac{\nu(\mc{S}_{\delta})\nu_dr^d}{2I(\mc{C}_{\sigma})} \cdot \ell \delta \tag{Step 2} \\
& \geq \frac{\dist(\mc{S}^{\delta},\mc{R}^{\delta})}{\rho L} \frac{\nu_dr^d\min\{\nu(\mc{S}^{\delta}),\nu(\mc{R}^{\delta})\}}{J(\mc{C}_{\sigma})}  \ell^2 \delta \tag{Step 3}\\
& \geq \frac{r (1 - 2\delta)\sqrt{2\pi}}{\rho L\sqrt{d + 2}} \frac{\nu_dr^d \min\{\nu(\mc{S}^{\delta}),\nu(\mc{R}^{\delta})\}}{J(\mc{C}_{\sigma})}  \ell^2 \delta \tag{Step 4} \\
& \geq  \frac{r (1 - 2\delta)\sqrt{2\pi}}{\rho L\sqrt{d + 2}} \min\bigl\{\wt{\pi}_{\nu,r}(\mc{S}^{\delta}),\wt{\pi}_{\nu,r}(\mc{R}^{\delta})\bigr\} \ell^2 \delta \tag{Step 2} \\
& \geq \frac{r (1 - 2\delta)\sqrt{2\pi}}{\rho L\sqrt{d + 2}} \min\bigl\{\wt{\pi}_{\nu,r}(\mc{S}),\wt{\pi}_{\nu,r}(\mc{R})\bigr\}   \ell^2 \delta (1 - a). \tag{by hypothesis}
\end{align*}
Setting $\delta = 1/3$, we have
\begin{equation*}
\wt{\Phi}_{\nu,r}(\mc{S}) \geq \min\biggl\{\frac{\sqrt{2\pi} r}{9\sqrt{d + 2} \rho L} \ell^2(1 - a), \frac{a\ell}{6}\biggr\}
\end{equation*}
and putting $a = r\ell/(2\rho)$ yields the claim.

Now, we turn to establishing the inequalities used in the above chain.

\paragraph{Step 1: Lower bound the ergodic flow.}
By symmetry, $\wt{Q}_{\nu,r}(\mc{S}_1,\mc{S}_2) = \wt{Q}_{\nu,r}(\mc{S}_1,\mc{S}_2)$, whence a direct computation yields
\begin{equation*}
2\wt{Q}_{\nu,r}(\mc{S}_1,\mc{S}_2) = \wt{Q}_{\nu,r}(\mc{S}_1,\mc{S}_2) + \wt{Q}_{\nu,r}(\mc{S}_2,\mc{S}_1) \geq \delta \wt{\pi}_{\nu,r}(\mc{S}_{\delta}).
\end{equation*}

\paragraph{Step 2: Estimate the stationary distribution.}

>>>>

\documentclass{article}
\usepackage{amsmath, amsfonts, amsthm, amssymb}
\usepackage{graphicx}
\usepackage[colorlinks]{hyperref}
\usepackage[parfill]{parskip}
\usepackage{algpseudocode}
\usepackage{algorithm}
\usepackage{enumerate}
\usepackage[shortlabels]{enumitem}
\usepackage{mathtools}
\usepackage{tikz}
\usepackage{verbatim}
\usepackage{fullpage}

@@

\DeclarePairedDelimiterX{\norm}[1]{\lVert}{\rVert}{#1}
\DeclarePairedDelimiterX{\seminorm}[1]{\lvert}{\rvert}{#1}

% Make a widecheck symbol (thanks, Stack Exchange!)
\DeclareFontFamily{U}{mathx}{\hyphenchar\font45}
\DeclareFontShape{U}{mathx}{m}{n}{
	<5> <6> <7> <8> <9> <10>
	<10.95> <12> <14.4> <17.28> <20.74> <24.88>
	mathx10
}{}
\DeclareSymbolFont{mathx}{U}{mathx}{m}{n}
\DeclareFontSubstitution{U}{mathx}{m}{n}
\DeclareMathAccent{\widecheck}{0}{mathx}{"71}
% widecheck made

\newcommand{\eqdist}{\ensuremath{\stackrel{d}{=}}}
\newcommand{\Graph}{\mathcal{G}}
\newcommand{\Reals}{\mathbb{R}}
\newcommand{\iid}{\overset{\text{i.i.d}}{\sim}}
\newcommand{\convprob}{\overset{p}{\to}}
\newcommand{\convdist}{\overset{w}{\to}}
\newcommand{\Expect}[1]{\mathbb{E}\left[ #1 \right]}
\newcommand{\Risk}[2][P]{\mathcal{R}_{#1}\left[ #2 \right]}
\newcommand{\Prob}[1]{\mathbb{P}\left( #1 \right)}
\newcommand{\iset}{\mathbf{i}}
\newcommand{\jset}{\mathbf{j}}
\newcommand{\myexp}[1]{\exp \{ #1 \}}
\newcommand{\abs}[1]{\left \lvert #1 \right \rvert}
\newcommand{\restr}[2]{\ensuremath{\left.#1\right|_{#2}}}
\newcommand{\ext}[1]{\widetilde{#1}}
\newcommand{\set}[1]{\left\{#1\right\}}
\newcommand{\seq}[1]{\set{#1}_{n \in \N}}
\newcommand{\floor}[1]{\left\lfloor #1 \right\rfloor}
\newcommand{\Var}{\mathrm{Var}}
\newcommand{\Cov}{\mathrm{Cov}}
\newcommand{\diam}{\mathrm{diam}}

\newcommand{\emC}{C_n}
\newcommand{\emCpr}{C'_n}
\newcommand{\emCthick}{C^{\sigma}_n}
\newcommand{\emCprthick}{C'^{\sigma}_n}
\newcommand{\emS}{S^{\sigma}_n}
\newcommand{\estC}{\widehat{C}_n}
\newcommand{\hC}{\hat{C^{\sigma}_n}}
\newcommand{\vol}{\mathrm{vol}}
\newcommand{\dist}{\mathrm{dist}}
\newcommand{\spansp}{\mathrm{span}~}
\newcommand{\1}{\mathbf{1}}

\newcommand{\Linv}{L^{\dagger}}
\DeclareMathOperator*{\argmin}{argmin}
\DeclareMathOperator*{\argmax}{argmax}

@@

%%% Vectors
\newcommand{\thetast}{\theta^{\star}}
\newcommand{\betap}{\beta^{(p)}}
\newcommand{\betaq}{\beta^{(q)}}
\newcommand{\vardeltapq}{\varDelta^{(p,q)}}
\newcommand{\lambdavec}{\boldsymbol{\lambda}}

%%% Matrices
\newcommand{\X}{X} % no bold
\newcommand{\Y}{Y} % no bold
\newcommand{\Z}{Z} % no bold
\newcommand{\Lgrid}{L_{\grid}}
\newcommand{\Dgrid}{D_{\grid}}
\newcommand{\Linvgrid}{L_{\grid}^{\dagger}}
\newcommand{\Lap}{L}
\newcommand{\NLap}{{\bf N}}
\newcommand{\PLap}{{\bf P}}
\newcommand{\Id}{I}

%%% Sets and classes
\newcommand{\Xset}{\mathcal{X}}
\newcommand{\Vset}{\mathcal{V}}
\newcommand{\Sset}{\mathcal{S}}
\newcommand{\Hclass}{\mathcal{H}}
\newcommand{\Pclass}{\mathcal{P}}
\newcommand{\Leb}{L}
\newcommand{\mc}[1]{\mathcal{#1}}

@@

%%% Operators
\newcommand{\Tadj}{T^{\star}}
\newcommand{\dive}{\mathrm{div}}
\newcommand{\dif}{\mathop{}\!\mathrm{d}}
\newcommand{\gradient}{\mathcal{D}}
\newcommand{\Hessian}{\mathcal{D}^2}
\newcommand{\dotp}[2]{\langle #1, #2 \rangle}
\newcommand{\Dotp}[2]{\Bigl\langle #1, #2 \Bigr\rangle}

%%% Misc
\newcommand{\grid}{\mathrm{grid}}
\newcommand{\critr}{R_n}
\newcommand{\dx}{\,dx}
\newcommand{\dy}{\,dy}
\newcommand{\dr}{\,dr}
\newcommand{\dxpr}{\,dx'}
\newcommand{\dypr}{\,dy'}
\newcommand{\wt}[1]{\widetilde{#1}}
\newcommand{\wh}[1]{\widehat{#1}}
\newcommand{\ol}[1]{\overline{#1}}
\newcommand{\spec}{\mathrm{spec}}
\newcommand{\LE}{\mathrm{LE}}
\newcommand{\LS}{\mathrm{LS}}
\newcommand{\SM}{\mathrm{SM}}
\newcommand{\OS}{\mathrm{OS}}
\newcommand{\PLS}{\mathrm{PLS}}

%%% Theorem environments
\newtheorem{theorem}{Theorem}
\newtheorem{conjecture}{Conjecture}
\newtheorem{lemma}{Lemma}
\newtheorem{example}{Example}
\newtheorem{corollary}{Corollary}
\newtheorem{proposition}{Proposition}
\newtheorem{assumption}{Assumption}
\newtheorem{remark}{Remark}

@@

\begin{document}
\title{Note on: Tightness of Upper Bounds on PPR Misclassification Error}
\author{Alden Green}
\date{\today}
\maketitle

\textbf{Setup}: We observe samples $x_1,\ldots,x_n \sim p$. For a given threshold $\lambda > 0$, we use a local clustering algorithm involving the PPR vector to recover an element $\mc{C}$ of the $\lambda$-upper-level-set of $p$. Letting $\mc{C}_{\sigma} = \mc{C} + B(0,\sigma)$, we obtain the following upper bound on the volume of the symmetric set difference $\Delta(\mc{C}_{\sigma}[X], \wh{C})  = \vol_{n,r}(\mc{C}_{\sigma}[X] \vartriangle \wh{C})$:
\begin{equation*}
\Delta(\mc{C}_{\sigma}[X], \wh{C}) \leq \underbrace{60}_{\textrm{PPR on a graph}} \cdot \underbrace{1028 \frac{\Lambda_{\sigma}^4 \rho^2 L^2 (d + 2)^3}{\lambda_{\sigma}^4 r^2} \log^2\biggl(c \frac{L\rho\Lambda_{\sigma}^{2/d}}{\lambda_{\sigma}^{2/d}r}\biggr)}_{\textrm{Upper bound on mixing time}} \cdot \underbrace{\frac{16}{9} \frac{dr\lambda(\lambda_{\sigma} - \theta r^{\gamma}/(\gamma + 1))}{\sigma \lambda_{\sigma}^2}}_{\textrm{Upper bound on normalized cut.}} \cdot (1 + c_\delta)
\end{equation*} 
with probability at least $1 - \delta$, for $n$ sufficiently large. The captions refer to the contribution to error of the three modular parts of our proof, which we detail next.

\section{PPR on a graph}
The following is essentially identical to Lemma 3.4 of~\textcolor{red}{(Zhu 2013)}, except with tighter constants.
\begin{lemma}
	\label{lem:zhu}
	Let $G = (V,E)$ be a undirected, unweighted, connected graph and let $p_v^{(\varepsilon)}$ be an $\varepsilon$-approximation to the PPR vector $p_v := p(v,\alpha;G)$. For $\beta \in (0,1)$,  the sweep cut $S_{\beta,v}$ is
	\begin{equation*}
	S_{\beta,v} = \set{u \in V: \frac{p_v^{(\varepsilon)}(u)}{\deg(u;G)} \geq \beta}.
	\end{equation*} 
	For some $A \subseteq V$, suppose that 
	\begin{equation*}
	\alpha \leq \min\Bigl\{\frac{1}{2000}, \frac{1}{2\tau_{\infty}(G[A])}\Bigr\},~~ \beta \leq \frac{1}{5\vol(A;G)},~~ \varepsilon \leq \frac{1}{25\vol(A;G)}
	\end{equation*}
	Then there exists a set $A^g \subset A$ with $\vol(A^g;G) \geq \frac{1}{2}\vol(A^g;G)$ such that for any $v \in A^g$, the sweep cut $S_{\beta,v}$ satisfies
	\begin{equation*}
	\vol(A \vartriangle S_{\beta,v};G) \leq 6\frac{\Phi(A;G)}{\alpha \beta}.
	\end{equation*}
\end{lemma}
I don't know how close to tight this is for a neighborhood graph.

\section{Mixing time}
We wish to upper bound the mixing time of a random walk over the subgraph $\wt{G}_{n,r} = G_{n,r}(\mc{C}_{\sigma}[X])$. Recall that our upper bound on mixing time for a general graph looks like
\begin{equation*}
\tau_{\infty}(G) \leq \frac{2}{\Phi^2(G)}\log(\mathrm{something}).
\end{equation*}
where $\Phi^2(G)$ is the conductance of $G$; I don't know how close this is to tight. We relate the sample conductance $\Phi(\wt{G}_{n,r})$ to the population conductance $\wt{\Phi}_{\Pbb,r}$ using some bounds on the optimal transport distance between $\mathbb{P}_n$ and $\mathbb{P}$, and in turn relate $\wt{\Phi}_{\Pbb,r}$ to the uniform conductance $\wt{\Phi}_{\nu,r}$ using the upper and lower bounds on density $p$ within $\mc{C}_{\sigma}$. Now I want to investigate of our lower bound on $\wt{\Phi}_{\nu,r}$, which is
\begin{equation*}
\wt{\Phi}_{\nu,r} \geq \frac{\sqrt{2\pi}}{36} \ell^2 \frac{r}{\rho L}
\end{equation*}

\subsection{Tightness of lower bound on }
Let's an accompanying upper bound on $\wt{\Phi}_{\nu,r}$. Let 
\begin{equation*}
\mc{C}_{\sigma} = [-\sigma,\sigma]^{d - 1} \otimes [-\rho/2,\rho/2],
\end{equation*}
and consider the partition of $\mc{C}_{\sigma}$ induced by the hyperplane $\{x \in \Rd: x_d = 0\}$, i.e
\begin{equation*}
\mc{L} = [-\sigma,\sigma]^{d - 1} \otimes [-\rho/2,0),~~\mc{R} = [-\sigma,\sigma]^{d - 1} \otimes [0,\rho/2].
\end{equation*}
Recalling that 
\begin{equation*}
\wt{\Phi}_{\nu,r}(\mc{L}) = \frac{\wt{Q}_{\nu,r}(\mc{L},\mc{R})}{\wt{\pi}_{\nu,r}(\mc{L})} = \frac{\int_{\mc{L}} \nu(B(x,r) \cap \mc{R}) \,dx}{\int_{\mc{L}} \nu(B(x,r) \cap \mc{C}_{\sigma}) \,dx} 
\end{equation*}
our goal will be to upper bound the numerator and lower bound the denominator of the above expression.
